---
title: "Exercise #6"
subtitle: "Fortgeschrittene Statistische Software für NF"
author: "Hyein Jeong (12449353)"
date: "`r Sys.Date()`"
output: distill::distill_article
---

## General Remarks

-   You can submit your solutions in teams of up to 3 students.
-   Include all your team-member's names and student numbers
    (Martrikelnummern) in the `authors` field.
-   Please use the exercise template document to work on and submit your
    results.
-   Use a level 2 heading for each new exercise and answer each subtask
    next to it's bullet point or use a new level 3 heading if you want.
-   Always render the R code for your solutions and make sure to include
    the resulting data in your rendered document.
    -   Make sure to not print more than 10 rows of data (unless
        specifically instructed to).
-   Always submit both the rendered document(s) as well as your source
    Rmarkdown document. Submit the files separately on moodle, **not**
    as a zip archive.
-   Make sure to submit you render your Rmarkdown as
    `distill:distill_article` and check the final output regarding any
    issues in formatting. Formatting errors may lead to point
    deductions.

## Exercise 1: Building an R package (20 Points)

For this exercise we ask you to build an R package. We do not ask you to
build any particular R package, but leave the choice of what your R
package will do up to you, to keep it more interesting for you.

Instead of having particular tasks for you to complete, we have a list
of requirements for your final R package and submission. Please submit
an Rmd and render it as always, although you will only have to provide
the short information asked for under *Submission*.

We advise you to start early with this exercise sheet and encourage you
to reach out if you encounter issues during the creation of your
package. For detailed information on all aspects of creating an R
package, we highlight again, the [great book on R
packages](https://r-pkgs.org/) by Hadley Wickham.

We look forward to seeing the cool packages you come up with and thank
you for participating in the course!

### Functionality

a)  Create a working R package that performs the task it is intended to
    do

b)  Your R package needs to be installable (test this before submitting)

c)  Your R package should contain at least 2 functions

d)  The functions in your R package should be properly documented
    according to the Roxygen convention. Each function should include an
    `@example` tag.

e)  The documentation for your package should be properly generated and
    up-to-date. After every change to the Roxygen comments of your
    functions, you will need to run `devtools::document()` again to do
    this.

f)  The `DESCRIPTION` file of your package should be properly formatted
    and contain all the required dependencies of your package. It should
    also provide an accurate `Title` and `Description` for your package.

### Submission

#### a)  Brief description of the package

This package is called ***datacleanR**. It provides functions to replace zeros with NAs, standardize numeric data, impute missing values, and remove outliers using the IQR method. I decided to build this package because these are common preprocessing steps I need for many data analysis tasks.

#### b)  GitHub Repository URL

Repository: `https://github.com/Heynii/datacleanR`

#### c)  Installation command

```{r}
remotes::install_github("Heynii/datacleanR")
```


### datacleanR Package Code

#### replace_zero_na

``` r
#' Replace zeros with NAs
#'
#' This function replaces all zeros in a numeric vector with NA values. 
#' Useful for sensor data where zero means missing.
#'
#' @param x A numeric vector
#' @return A numeric vector with zeros replaced by NAs
#' @examples
#' replace_zero_na(c(0, 1, 2, 0, 3))
#'
#' @export
replace_zero_na <- function(x) {
  # Functionality: replace 0 with NA
  x[x == 0] <- NA
  return(x)
}
```

#### standardize

``` r
#' Standardize numeric vector
#'
#' @param x Numeric vector
#' @return Standardized numeric vector (mean 0, sd 1)
#' @examples
#' standardize(c(1,2,3,4,5))
#' @export
standardize <- function(x) {
  (x - mean(x, na.rm=TRUE)) / sd(x, na.rm=TRUE)
}
```

#### impute_na

``` r
#' Impute missing values
#'
#' @param x Numeric vector
#' @param method Method: "mean", "median" or numeric value
#' @return Numeric vector with imputed values
#' @examples
#' impute_na(c(1,NA,3), method="mean")
#' impute_na(c(1,NA,3), method=0)
#' @export
impute_na <- function(x, method="mean") {
  if(method=="mean") {
    val <- mean(x, na.rm=TRUE)
  } else if(method=="median") {
    val <- median(x, na.rm=TRUE)
  } else if(is.numeric(method)) {
    val <- method
  } else {
    stop("Invalid method")
  }
  x[is.na(x)] <- val
  return(x)
}
```

#### remove_outliers

``` r
#' Remove outliers with IQR
#'
#' @param x Numeric vector
#' @return Numeric vector with outliers set to NA
#' @examples
#' remove_outliers(c(1,2,3,100))
#' @export
remove_outliers <- function(x) {
  Q1 <- quantile(x,0.25,na.rm=TRUE)
  Q3 <- quantile(x,0.75,na.rm=TRUE)
  IQR <- Q3 - Q1
  lower <- Q1 - 1.5*IQR
  upper <- Q3 + 1.5*IQR
  x[x < lower | x > upper] <- NA
  return(x)
}
```

### NAMESPACE

```r
export(replace_zero_na)
export(standardize)
export(impute_na)
export(remove_outliers)
```

### Package development workflow

After writing or editing the roxygen documentation in each function, I will run the following command to regenerate the help files and the NAMESPACE file:


```{r}
devtools::document()
```



